checkData

### 2023-08-29 analysis/checkData.Rmd
Update checkData.Rmd
moved initial processing of raw data files to raw_to_primary.R
this script now loads in the primary data files

```{r}
# article data (random)
d_articles_random <- read_csv(here('data','raw','articles (random) - Sheet1.csv'), show_col_types = F) %>%
  filter(!is.na(`primary coder initials`) & !is.na(`secondary coder initials`)) # we only need articles that were coded by someone

# article data (prominent)
d_articles_prominent <- read_csv(here('data','raw','articles (prominent) - Sheet1.csv'), show_col_types = F)  %>%
  filter(!is.na(`primary coder initials`) & !is.na(`secondary coder initials`)) # we only need articles that were coded by someone

# journal data (random and prominent sample)
d_journals <- read_csv(here('data','raw','Data Extraction Form (policy) (Responses) - Form Responses 1.csv'), show_col_types = F)
```

@@

d_articles_random <- d_articles_random %>%
  select(
    article_id = `article id`,
    coder_id_primary = `primary coder initials`,
    coder_id_secondary = `secondary coder initials`,
    exclusion_primary = `1_exclusion`,
    exclusion_reason_primary = `1_exclusionReason`,
    ppc_linked_primary = `1_Is article linked to PPC`,
    notes_primary = `1_Additional notes`,
    exclusion_secondary = `2_exclusion`,
    exclusion_reason_secondary = `2_exclusionReason`,
    ppc_linked_secondary = `2_Is article linked to PPC`,
    notes_secondary = `2_Additional notes`
  )

d_articles_prominent <- d_articles_prominent %>%
  select(
    article_id = `article id`,
    coder_id_primary = `primary coder initials`,
    coder_id_secondary = `secondary coder initials`,
    exclusion_primary = `1_exclusion`,
    exclusion_reason_primary = `1_exclusionReason`,
    ppc_linked_primary = `1_Is article linked to PPC`,
    notes_primary = `1_Additional notes`,
    exclusion_secondary = `2_exclusion`,
    exclusion_reason_secondary = `2_exclusionReason`,
    ppc_linked_secondary = `2_Is article linked to PPC`,
    notes_secondary = `2_Additional notes`
  )
```

@@

Check every row has a `journal` that appears in the original random or prominent sample lists. We initially get an error for this test because some journal names were entered in the extraction form with incorrect formatting. Correct this below before running the test.

@@

```{r}
assert_that(
  all(d_journals$journal %in% c(journal_list_prominent$Journal, journal_list_random$Journal)),
  msg = "Found journal names that do not match sample"
)
```

That fixed the problem, now all journal names in the extracted data match journal names in the sample files.

@@

Firstly let's join the prominent and random articles together (with a new column identifying which sample they are in) to streamline some testing.

```{r}
d_articles <- bind_rows(
  d_articles_random %>% mutate(sampleID = "random"),
  d_articles_prominent %>% mutate(sampleID = "prominent")
)
```

>>>>

```{r}
d_articles <- read_csv(here('data','primary','articles.csv'), show_col_types = F) # article data 
d_journals <- read_csv(here('data','primary','journals.csv'), show_col_types = F) # journal data 
```

@@

d_articles <- d_articles %>%
  select(
    article_id = `article id`,
    coder_id_primary = `primary coder initials`,
    coder_id_secondary = `secondary coder initials`,
    exclusion_primary = `1_exclusion`,
    exclusion_reason_primary = `1_exclusionReason`,
    ppc_linked_primary = `1_Is article linked to PPC`,
    notes_primary = `1_Additional notes`,
    exclusion_secondary = `2_exclusion`,
    exclusion_reason_secondary = `2_exclusionReason`,
    ppc_linked_secondary = `2_Is article linked to PPC`,
    notes_secondary = `2_Additional notes`
  )
```

@@

Some journal names were entered in the extraction form with incorrect formatting. Correct this below before running the test.

@@

@@
